Designing a high-performance boundary element library with OpenCL and Numba

### 2021-04-13 performance.tex
Updated image files with the right font

\begin{figure}
	\center
	\includegraphics[width=6cm]{img/intel_pocl_laplace_comp}
	\caption{Comparison of the performance of POCL and the Intel OpenCL runtime for the assembly of the Laplace single-layer boundary operator on a grid with 32,768 elements.}
	\label{fig:intel_pocl_laplace_cmp}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=7cm]{img/pocl_single_layer}
	\caption{Comparison of the single-precision and double-precision performance for various grid sizes using Pocl and P0 basis functions.}
	\label{fig:pocl_single_layer}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=7cm]{img/efield_domain_potential}
	\caption{Evaluation of an electric field potential operator on CPU via POCL vs GPU}
	\label{fig:efield_domain_potential}
\end{figure}

>>>>

\begin{figure}
	\center
	\includegraphics[width=6cm]{img/intel_pocl_laplace_comp.pdf}
	\caption{Comparison of the performance of POCL and the Intel OpenCL runtime for the assembly of the Laplace single-layer boundary operator on a grid with 32,768 elements.}
	\label{fig:intel_pocl_laplace_cmp}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=7cm]{img/pocl_single_layer.pdf}
	\caption{Comparison of the single-precision and double-precision performance for various grid sizes using Pocl and P0 basis functions.}
	\label{fig:pocl_single_layer}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=7cm]{img/efield_domain_potential.pdf}
	\caption{Evaluation of an electric field potential operator on CPU via POCL vs GPU}
	\label{fig:efield_domain_potential}
\end{figure}
